Future Directions

### 2021-03-07 manuscripts/laplacian_smoothing/arXiv/appendix.tex
Changed proof of Lemma 4 in response to Siva's comment.

In Lemma~\ref{lem:linear_smoother_fixed_graph_testing}, we upper bound the error of a test involving the statistic $\|\wc{f}\|_2^2 = {\bf Y}^{\top} S^2 {\bf Y}$.
\begin{lemma}
	\label{lem:linear_smoother_fixed_graph_testing}
	Let $\wc{T} = Y^{\top} S^2 Y$ for a square, symmetric matrix $S \in \Reals^{n \times n}$. Define the threshold $\wc{t}_b$ to be 
	\begin{equation}
	\wc{t}_{b} := \norm{\lambdavec(S)}_2^2 + 2b \norm{\lambdavec(S)}_4^2.
	\end{equation}
	It holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_typeI}
		\Pbb_0\bigl(\wc{T} > \wc{t}_b\bigr) \leq \frac{1}{b^2}.
		\end{equation}
		\item \textbf{Type II error.} Under the further assumption
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_critical_radius}
		f_0^{\top} S^2 f_0 \geq 4b \norm{\lambdavec(S)}_4^2,
		\end{equation}
		then
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_typeII}
		\Pbb_{f_0}\bigl(\wc{T} \leq \wc{t}_b\bigr) \leq \frac{4}{b^2} + \frac{8}{b \norm{\lambdavec(S)}_4^{2}}.
		\end{equation}
	\end{itemize}
\end{lemma}

@@

\textit{Variance.} Starting from \eqref{pf:linear_smoother_fixed_graph_testing1} and recalling $\Var(Z_k^2) = 2$, we derive
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing_var}
\Var_{f_0}\bigl[\wc{T}\bigr] \leq 8 f_0^{\top} S^4 f_0 + 4 \sum_{k = 1}^{n} \bigl(\lambda_k(S)\bigr)^4.
\end{equation}

\textit{Bounding Type I and Type II error.} The upper bound \eqref{eqn:linear_smoother_fixed_graph_testing_typeI} follows immediately from \eqref{pf:linear_smoother_fixed_graph_testing_mean}, \eqref{pf:linear_smoother_fixed_graph_testing_var}, and Chebyshev's inequality.

The bound \eqref{eqn:linear_smoother_fixed_graph_testing_typeII} also follows from Chebyshev's inequality, as can be seen by the following manipulations,
\begin{equation*}
\begin{aligned}
\Pbb_{f_0}\Bigl(\wc{T} \leq \wc{t}_b\Bigr) & = \Pbb_{f_0}\Bigl(\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr] \leq \wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr) \\
& \overset{(i)}{\leq} \Pbb_{f_0}\Bigl(\Bigl|\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr| \geq \Bigl|\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr|\Bigr) \leq \frac{\Var_{f_0}\bigl[\wc{T}\bigr]}{\bigl(\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\bigr)^2} \\ 
& \overset{(ii)}{\leq} 4 \frac{\Var_{f_0}\bigl[\wc{T}\bigr]}{(f_0^{\top} S^2 f_0)^2} \\
& \overset{(iii)}{\leq} \frac{32}{f_0^{\top} S^2 f_0} + \frac{4}{b^2} \\
& \overset{(iv)}{\leq} \frac{8}{b} \Biggl(\sum_{k = 1}^{n}\bigl(\lambda_k(S)\bigr)^4\Biggr)^{-1/2} + \frac{4}{b^2}
\end{aligned}
\end{equation*}
In the previous expression, $(i)$ and $(ii)$ follow since assumption \eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius} and equation \eqref{pf:linear_smoother_fixed_graph_testing_mean} together imply 
\begin{equation*}
\wc{t}_b - \Ebb_{f_0}[\wc{T}] = f_0^{\top} S^2 f_0 - 2b\|{\bf \lambda}(S)\|_4^2 \geq \frac{1}{2}f_0^{\top} S^2 f_0
\end{equation*}
\sbcomment{I think the first equality should be the negative of what you wrote?}
$(iii)$ follows from assumption \eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius} and the inequality \eqref{pf:linear_smoother_fixed_graph_testing_var}, and $(iv)$ follows from \eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius}.

\subsection{Analysis of Laplacian smoothing}

Upper bounds on the mean squared error of $\wh{f}$, and Type I and Type II error of $\wh{T}$, follow from setting $S = (\rho L + I)^{-1}$ in Lemmas~\ref{lem:linear_smoother_fixed_graph_estimation} and~\ref{lem:linear_smoother_fixed_graph_testing}. We give these results in Lemma~\ref{lem:ls_fixed_graph_estimation} and~\ref{lem:ls_fixed_graph_testing}, and prove them immediately. Recall that $\lambda_1,\ldots,\lambda_n$ are the $n$ eigenvalues of $\Lap$ (sorted in ascending order).
\begin{lemma}
	\label{lem:ls_fixed_graph_estimation}
	For any $\rho > 0$,
	\begin{equation}
	\label{eqn:ls_fixed_graph_estimation_prob}
	\frac{1}{n}\bigl\|\wh{f} - f_0\bigr\|_2^2 \leq \frac{2\rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{10}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_{k} + 1\bigr)^2}
	\end{equation}
	with probability at least $1 - \exp\Bigl(-\sum_{k = 1}^{n}\bigl(\rho \lambda_k + 1\bigr)^{-2}\Bigr)$.
\end{lemma}
Recall that 
\begin{equation*}
\wh{t}_b := \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^2} + \frac{2b}{n}\sqrt{\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^4}}.
\end{equation*}
\begin{lemma}
	\label{lem:ls_fixed_graph_testing}
	For any $\rho > 0$ and any $b \geq 1$, it holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeI}
		\Pbb_0\Bigl(\wh{T} > \wh{t}_b\Bigr) \leq \frac{1}{b^2}
		\end{equation}
		\item \textbf{Type II error.} If
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_critical_radius}
		\frac{1}{n}\norm{f_0}_2^2 \geq \frac{2 \rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{4b}{n} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{1/2}
		\end{equation}
		then
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeII}
		\Pbb_{f_0}\Bigl(\wh{T}(G) \leq \wh{t}_b\Bigr) \leq \frac{4}{b^2} + \frac{8}{b} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}
		\end{equation}
	\end{itemize}
\end{lemma}

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_estimation}.}
Let $\wh{S} = (\Id + \rho \Lap)^{-1}$, the estimator $\wh{f} = \wh{S}Y$, and
\begin{equation*}
\bigl\|\lambdavec(\wh{S})\bigr\|_2^2 = \sum_{k = 1}^{n} \frac{1}{\bigl(1 + \rho \lambda_k\bigr)^2}.
\end{equation*} 
We deduce the following upper bound on the bias term,
\begin{equation*}
\begin{aligned}
\bigl\|(\wh{S} - I)f_0\bigr\|_2^2 & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\bigl(\wh{S} - \Id\bigr) \Lap^{-1/2} \Lap^{1/2} f_0 \\
& \leq f_0^{\top} \Lap f_0 \cdot \lambda_n\Bigl(\Lap^{-1/2}\bigl(\wh{S} - \Id\bigr)\Lap^{-1/2}\Bigr) \\
& = f_0^{\top} \Lap f_0 \cdot \max_{k \in [n]} \biggl\{\frac{1}{\lambda_k} \Bigl(1 - \frac{1}{\rho\lambda_k + 1}\Bigr) \biggr\} \\
& = f_0^{\top} \Lap f_0 \cdot \rho.
\end{aligned}
\end{equation*} 
In the above, we have written $\Lap^{-1/2}$ for the square root of the pseudoinverse of $\Lap$, and the maximum is over all indices $k$ such that $\lambda_k > 0$. The claim of the Lemma then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_estimation}.

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_testing}.}
Let $\wh{S} := (\rho \Lap + \Id)^{-1}$, and note that $\wh{T} = \frac{1}{n}{\bf Y}^{\top} \wh{S}^2 {\bf Y}$. The bound on Type I error \eqref{eqn:ls_fixed_graph_testing_typeI} follows immediately from \eqref{eqn:linear_smoother_fixed_graph_testing_typeI}. 
To establish the bound on Type II error, we must lower bound $f_0^{\top} \wh{S}^2 f_0$. We first note that by assumption \eqref{eqn:ls_fixed_graph_testing_critical_radius},
\begin{align*}
f_0^{\top} \wh{S}^2 f_0 & = \bigl\|f_0\bigr\|_2^2 - f_0^{\top}(I - \wh{S}^2)f_0 \\
& \geq 2 \rho \bigl(f_0^{\top} \Lap f_0\bigr) - f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0 + 4b \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}.
\end{align*}
Upper bounding $f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0$ as follows:
\begin{equation*}
\begin{aligned}
f_0^{\top} \Bigl(\Id - \wh{S}^2\Bigr) f_0  & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2} \Lap^{1/2} f_0 \\ 
& \leq f_0^{\top} \Lap f_0 \cdot  \lambda_{n}\biggl(\Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2}\biggr) \\ 
& \overset{(i)}{=}  f_0^{\top} \Lap f_0 \cdot \max_{k} \biggl\{ \frac{1}{\lambda_k} \Bigl(1 - \frac{1}{(\rho \lambda_k + 1)^2}\Bigr) \biggr\} \\
& \overset{(ii)}{\leq} f_0^{\top} \Lap f_0 \cdot 2\rho,
\end{aligned}
\end{equation*}
---where in the above the maximum is over all indices $k$ such that $\lambda_k > 0$, and the last inequality follows from the basic algebraic identity $1 - 1/(1 + x)^2 \leq 2 x$ for any $x > 0$---we deduce that
\begin{equation*}
f_0^{\top} \wh{S}^2 f_0 \geq 2b \biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \biggr)^{-1/2}.
\end{equation*} 
The upper bound on Type II error \eqref{eqn:ls_fixed_graph_testing_typeII} then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_testing}.

@@

Since
\begin{equation*}
f^{\top} \Lap_{n,r} f = \frac{1}{2}\sum_{i, j = 1}^{n} \bigl(f(X_i) - f(X_j)\bigr)^2 W_{ij},
\end{equation*}
it follows that
\begin{equation}
\label{pf:first_order_graph_sobolev_seminorm_1}
\Ebb\Bigl[f^{\top} \Lap_{n,r} f\Bigr] = \frac{n(n - 1)}{2} \Ebb\biggl[\Bigl(f(X') - f(X)\Bigr)^2 K\biggl(\frac{\|X' - X\|}{r}\biggr)\biggr]
\end{equation}
where $X$ and $X'$ are random variables independently drawn from $P$.

@@

Obviously
\begin{equation}
\Ebb\biggl[\bigl(f(X') - f(X)\bigr)^2K\biggl(\frac{\|X' - X\|}{r}\biggr)\biggr] \leq p_{\max}^2 \int_{\Xset} \int_{\Xset} \bigl(f(x') - f(x)\bigr)^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dx' \,dx, \label{pf:first_order_graph_sobolev_seminorm_2}
\end{equation}
so that it remains now to bound the double integral. Replacing difference by integrated derivative as in \eqref{pf:first_order_graph_sobolev_seminorm_1.5}, we obtain
\begin{align}
\int_{\Xset} \int_{\Xset} \bigl(f(x') - f(x)\bigr)^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dx' \,dx & = \int_{\Xset} \int_{\Xset} \biggl[\int_{0}^{1} \nabla f\bigl(x + t(x' - x)\bigr)^{\top} (x' - x)\,dt\biggr]^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dx' \,dx \nonumber \\
& \overset{(i)}{\leq} \int_{\Xset} \int_{\Xset} \int_{0}^{1} \biggl[\nabla f\bigl(x + t(x' - x)\bigr)^{\top} (x' - x)\biggr]^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dt\,dx' \,dx \nonumber \\
& \overset{(ii)}{\leq} r^{d + 2} \int_{\Xset} \int_{B(0,1)} \int_{0}^{1} \biggl[\nabla f\bigl(x + trz\bigr)^{\top} z\biggr]^2 K\bigl(\|z\|\bigr) \,dt\,dz \,dx \nonumber \\
&  \overset{(iii)}{\leq} r^{d + 2} \int_{\Omega} \int_{B(0,1)} \int_{0}^{1} \Bigl[\nabla f\bigl(\wt{x}\bigr)^{\top} z\Bigr]^2 K\bigl(\|z\|\bigr) \,dt \,dz \,d\wt{x} \label{pf:first_order_graph_sobolev_seminorm_3} 
\end{align}
where $(i)$ follows by Jensen's inequality, $(ii)$ follows by substituting $z = (x' - x)/r$ and~\ref{asmp:kernel}, and $(iii)$ by exchanging integrals, substituting $\wt{x} = x + trz$, and noting that $x \in \mc{X}$ implies that $\wt{x} \in \Omega$.

@@

Suppose $f$ satisfies $|f(x') - f(x)| \leq M \|x - x\|$ for all $x,x' \in \mc{X}$. Then we can strengthen the high probability bound in Lemma~\ref{lem:graph_sobolev_seminorm} from $1 - \delta$ to $1 - \delta^2/n$, at the cost of only a constant factor in the upper bound on $f^{\top} \Lap_{n,r} f$.
\begin{proposition}
	\label{prop:graph_sobolev_seminorm_lipschitz}
	Let $r \geq C_0(\log n/n)^{1/d}$. For any $f$ such that $|f(x') - f(x)| \leq M \|x - x\|$ for all $x,x' \in \mc{X}$, with probability at least $1 - C\delta^2/n$ it holds that
	\begin{equation*}
	f^{\top} \Lap_{n,r} f \leq \biggl(\frac{1}{\delta} + C_2\biggr) n^2 r^{d + 2} M^2
	\end{equation*}
\end{proposition}

>>>>

In Lemma~\ref{lem:linear_smoother_fixed_graph_testing}, we upper bound the error of a test involving the statistic $\|\wc{f}\|_2^2 = {\bf Y}^{\top} S^2 {\bf Y}$. We will require that $S$ be a \emph{contraction}, meaning that it has operator norm no greater than $1$, $\|Sv\|_2 \leq \|v\|_2$ for all $v \in \Reals^n$.
\begin{lemma}
	\label{lem:linear_smoother_fixed_graph_testing}
	Let $\wc{T} = {\bf Y}^{\top} S^2 {\bf Y}$ for a square, symmetric matrix $S \in \Reals^{n \times n}$. Suppose $S$ is a contraction. Define the threshold $\wc{t}_b$ to be 
	\begin{equation}
	\label{eqn:linear_smoother_fixed_graph_threshold}
	\wc{t}_{b} := \norm{\lambdavec(S)}_2^2 + 2b \norm{\lambdavec(S)}_4^2.
	\end{equation}
	It holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_typeI}
		\Pbb_0\bigl(\wc{T} > \wc{t}_b\bigr) \leq \frac{1}{b^2}.
		\end{equation}
		\item \textbf{Type II error.} Under the further assumption
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_critical_radius}
		f_0^{\top} S^2 f_0 \geq 4b \norm{\lambdavec(S)}_4^2,
		\end{equation}
		then
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_typeII}
		\Pbb_{f_0}\bigl(\wc{T} \leq \wc{t}_b\bigr) \leq \frac{4}{b^2} + \frac{8}{b \norm{\lambdavec(S)}_4^{2}}.
		\end{equation}
	\end{itemize}
\end{lemma}

@@

\textit{Variance.} We start from \eqref{pf:linear_smoother_fixed_graph_testing1}. Recalling that $\Var(Z_k^2) = 2$, it follows from the Cauchy-Schwarz inequality that
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing_var}
\Var_{f_0}\bigl[\wc{T}\bigr] \leq 8 f_0^{\top} S^4 f_0 + 4 \sum_{k = 1}^{n} \bigl(\lambda_k(S)\bigr)^4.
\end{equation}

\textit{Bounding Type I and Type II error.} The upper bound \eqref{eqn:linear_smoother_fixed_graph_testing_typeI} on Type I error follows immediately from \eqref{pf:linear_smoother_fixed_graph_testing_mean}, \eqref{pf:linear_smoother_fixed_graph_testing_var}, and Chebyshev's inequality.

We now establish the upper bound~\eqref{eqn:linear_smoother_fixed_graph_testing_typeII} on Type II error. From assumption~\eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius}, we see that $f_0^{\top} S^2 f_0^{\top} - \wc{t}_b \leq 0$. As a result,
\begin{align*}
\Pbb_{f_0}\Bigl(\wc{T} \leq \wc{t}_b\Bigr) & = \Pbb_{f_0}\Bigl(\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr] \leq \wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr) \\ 
& \leq \Pbb_{f_0}\Bigl(\Bigl|\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr| \geq \Bigl|\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr|\Bigr) \\ 
& \leq \frac{\Var_{f_0}\bigl[\wc{T}\bigr]}{\bigl(\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\bigr)^2},
\end{align*}
where the last line follows from Chebyshev's inequality. Plugging in the expressions~\eqref{pf:linear_smoother_fixed_graph_testing_mean} and~\eqref{pf:linear_smoother_fixed_graph_testing_var} for the mean and variance of $\wc{T}$, as well as the definition of $\wc{t}_b$ in~\eqref{eqn:linear_smoother_fixed_graph_threshold}, we obtain that
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing2}
\Pbb_{f_0}\Bigl(\wc{T} \leq \wc{t}_b\Bigr) \leq \frac{4\|\lambdavec(S)\|_4^4}{\bigl(f_0^{\top}S^2f_0 - 2b \norm{\lambdavec(S)}_4^2\bigr)^2} + \frac{8f_0^{\top}S^4f_0 }{\bigl(f_0^{\top}S^2f_0 - 2b \norm{\lambdavec(S)}_4^2\bigr)^2}.
\end{equation}
We now use the assumed lower bound $f_0^{\top} S^2 f_0 \geq 4b \norm{\lambdavec(S)}_4^2$ to separately upper bound each of the two terms on the right hand side of~\eqref{pf:linear_smoother_fixed_graph_testing2}. It follows immediately that
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing2.5}
\frac{4 \|\lambdavec(S)\|_4^4}{\bigl(f_0^{\top}S^2f_0 - 2b \norm{\lambdavec(S)}_4^2\bigr)^2} \leq \frac{1}{b^2},
\end{equation}
giving a sufficient upper bound on the first term. Now we upper bound the second term,
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing3}
\frac{8f_0^{\top}S^4f_0 }{\bigl(f_0^{\top}S^2f_0 - 2b \norm{\lambdavec(S)}_4^2\bigr)^2} \leq \frac{32 f_0^{\top}S^4f_0 }{\bigl(f_0^{\top}S^2f_0\bigr)^2} \leq \frac{8}{b \|\lambdavec(S)\|_4^2} \frac{f_0^{\top}S^4f_0 }{f_0^{\top}S^2f_0} \leq \frac{8}{b \|\lambdavec(S)\|_4^2},
\end{equation}
where the final inequality is satisfied because $S$ is a contraction. Plugging~\eqref{pf:linear_smoother_fixed_graph_testing2.5} and~\eqref{pf:linear_smoother_fixed_graph_testing3} back into~\eqref{pf:linear_smoother_fixed_graph_testing2} then gives the desired result.

\sbcomment{I think the first equality should be the negative of what you wrote?}

\agcomment{You were correct. However I also rewrote the proof a bit to make it (hopefully) easier to follow. We also need that $S$ is a contraction---a condition that I had and then deleted at some point by accident--- and I added this to the statement of the Lemma.}
\subsection{Analysis of Laplacian smoothing}

Upper bounds on the mean squared error of $\wh{f}$, and Type I and Type II error of $\wh{T}$, follow from setting $S = (\rho L + I)^{-1}$ in Lemmas~\ref{lem:linear_smoother_fixed_graph_estimation} and~\ref{lem:linear_smoother_fixed_graph_testing}. We give these results in Lemma~\ref{lem:ls_fixed_graph_estimation} and~\ref{lem:ls_fixed_graph_testing}, and prove them immediately. Recall that $\lambda_1,\ldots,\lambda_n$ are the $n$ eigenvalues of $\Lap$ (sorted in ascending order).
\begin{lemma}
	\label{lem:ls_fixed_graph_estimation}
	For any $\rho > 0$,
	\begin{equation}
	\label{eqn:ls_fixed_graph_estimation_prob}
	\frac{1}{n}\bigl\|\wh{f} - f_0\bigr\|_2^2 \leq \frac{2\rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{10}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_{k} + 1\bigr)^2},
	\end{equation}
	with probability at least $1 - \exp\Bigl(-\sum_{k = 1}^{n}\bigl(\rho \lambda_k + 1\bigr)^{-2}\Bigr)$.
\end{lemma}
Recall that 
\begin{equation*}
\wh{t}_b := \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^2} + \frac{2b}{n}\sqrt{\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^4}}.
\end{equation*}
\begin{lemma}
	\label{lem:ls_fixed_graph_testing}
	For any $\rho > 0$ and any $b \geq 1$, it holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeI}
		\Pbb_0\Bigl(\wh{T} > \wh{t}_b\Bigr) \leq \frac{1}{b^2}.
		\end{equation}
		\item \textbf{Type II error.} If
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_critical_radius}
		\frac{1}{n}\norm{f_0}_2^2 \geq \frac{2 \rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{4b}{n} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{1/2},
		\end{equation}
		then
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeII}
		\Pbb_{f_0}\Bigl(\wh{T}(G) \leq \wh{t}_b\Bigr) \leq \frac{4}{b^2} + \frac{8}{b} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}.
		\end{equation}
	\end{itemize}
\end{lemma}

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_estimation}.}
Let $\wh{S} = (\Id + \rho \Lap)^{-1}$, the estimator $\wh{f} = \wh{S}Y$, and
\begin{equation*}
\bigl\|\lambdavec(\wh{S})\bigr\|_2^2 = \sum_{k = 1}^{n} \frac{1}{\bigl(1 + \rho \lambda_k\bigr)^2}.
\end{equation*} 
We deduce the following upper bound on the bias term,
\begin{equation*}
\begin{aligned}
\bigl\|(\wh{S} - I)f_0\bigr\|_2^2 & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\bigl(\wh{S} - \Id\bigr)^2 \Lap^{-1/2} \Lap^{1/2} f_0 \\
& \leq f_0^{\top} \Lap f_0 \cdot \lambda_n\Bigl(\Lap^{-1/2}\bigl(\wh{S} - \Id\bigr)^2 \Lap^{-1/2}\Bigr) \\
& = f_0^{\top} \Lap f_0 \cdot \max_{k \in [n]} \biggl\{\frac{1}{\lambda_k} \Bigl(1 - \frac{1}{\rho\lambda_k + 1}\Bigr)^2 \biggr\} \\
& \leq f_0^{\top} \Lap f_0 \cdot \rho.
\end{aligned}
\end{equation*} 
In the above, we have written $\Lap^{-1/2}$ for the square root of the pseudoinverse of $\Lap$, and the maximum is over all indices $k$ such that $\lambda_k > 0$. The claim of the Lemma then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_estimation}.

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_testing}.}
Let $\wh{S} := (I + \rho L)^{-1}$, so that $\wh{T} = \frac{1}{n}{\bf Y}^{\top} \wh{S}^2 {\bf Y}$. Note that $\wh{S}$ is a contraction, so that we may invoke Lemma~\ref{lem:linear_smoother_fixed_graph_testing}. The bound on Type I error \eqref{eqn:ls_fixed_graph_testing_typeI} follows immediately from \eqref{eqn:linear_smoother_fixed_graph_testing_typeI}. 
To establish the bound on Type II error, we must lower bound $f_0^{\top} \wh{S}^2 f_0$. We first note that by assumption \eqref{eqn:ls_fixed_graph_testing_critical_radius},
\begin{align*}
f_0^{\top} \wh{S}^2 f_0 & = \bigl\|f_0\bigr\|_2^2 - f_0^{\top}(I - \wh{S}^2)f_0 \\
& \geq 2 \rho \bigl(f_0^{\top} \Lap f_0\bigr) - f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0 + 4b \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}.
\end{align*}
Upper bounding $f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0$ as follows:
\begin{equation*}
\begin{aligned}
f_0^{\top} \Bigl(\Id - \wh{S}^2\Bigr) f_0  & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2} \Lap^{1/2} f_0 \\ 
& \leq f_0^{\top} \Lap f_0 \cdot  \lambda_{n}\biggl(\Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2}\biggr) \\ 
& = f_0^{\top} \Lap f_0 \cdot \max_{k} \biggl\{ \frac{1}{\lambda_k} \Bigl(1 - \frac{1}{(\rho \lambda_k + 1)^2}\Bigr) \biggr\} \\
& \leq f_0^{\top} \Lap f_0 \cdot 2\rho,
\end{aligned}
\end{equation*}
---where in the above the maximum is over all indices $k$ such that $\lambda_k > 0$, and the last inequality follows from the basic algebraic identity $1 - 1/(1 + x)^2 \leq 2 x$ for any $x > 0$---we deduce that
\begin{equation*}
f_0^{\top} \wh{S}^2 f_0 \geq 4b \biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \biggr)^{-1/2}.
\end{equation*} 
The upper bound on Type II error \eqref{eqn:ls_fixed_graph_testing_typeII} then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_testing}.

@@

Since
\begin{equation*}
f^{\top} \Lap_{n,r} f = \frac{1}{2}\sum_{i, j = 1}^{n} \bigl(f(X_i) - f(X_j)\bigr)^2 W_{ij},
\end{equation*}
it follows that
\begin{equation}
\label{pf:first_order_graph_sobolev_seminorm_1}
\Ebb\Bigl[f^{\top} \Lap_{n,r} f\Bigr] = \frac{n(n - 1)}{2} \Ebb\biggl[\Bigl(f(X') - f(X)\Bigr)^2 K\biggl(\frac{\|X' - X\|}{r}\biggr)\biggr],
\end{equation}
where $X$ and $X'$ are random variables independently drawn from $P$.

@@

Obviously
\begin{equation}
\Ebb\biggl[\bigl(f(X') - f(X)\bigr)^2K\biggl(\frac{\|X' - X\|}{r}\biggr)\biggr] \leq p_{\max}^2 \int_{\Xset} \int_{\Xset} \bigl(f(x') - f(x)\bigr)^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dx' \,dx, \label{pf:first_order_graph_sobolev_seminorm_2}
\end{equation}
so that it remains now to bound the double integral. Replacing difference by integrated derivative as in \eqref{pf:first_order_graph_sobolev_seminorm_1.5}, we obtain
\begin{align}
\int_{\Xset} \int_{\Xset} \bigl(f(x') - f(x)\bigr)^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dx' \,dx & = \int_{\Xset} \int_{\Xset} \biggl[\int_{0}^{1} \nabla f\bigl(x + t(x' - x)\bigr)^{\top} (x' - x)\,dt\biggr]^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dx' \,dx \nonumber \\
& \overset{(i)}{\leq} \int_{\Xset} \int_{\Xset} \int_{0}^{1} \biggl[\nabla f\bigl(x + t(x' - x)\bigr)^{\top} (x' - x)\biggr]^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dt\,dx' \,dx \nonumber \\
& \overset{(ii)}{\leq} r^{d + 2} \int_{\Xset} \int_{B(0,1)} \int_{0}^{1} \biggl[\nabla f\bigl(x + trz\bigr)^{\top} z\biggr]^2 K\bigl(\|z\|\bigr) \,dt\,dz \,dx \nonumber \\
&  \overset{(iii)}{\leq} r^{d + 2} \int_{\Omega} \int_{B(0,1)} \int_{0}^{1} \Bigl[\nabla f\bigl(\wt{x}\bigr)^{\top} z\Bigr]^2 K\bigl(\|z\|\bigr) \,dt \,dz \,d\wt{x}, \label{pf:first_order_graph_sobolev_seminorm_3} 
\end{align}
where $(i)$ follows by Jensen's inequality, $(ii)$ follows by substituting $z = (x' - x)/r$ and~\ref{asmp:kernel}, and $(iii)$ by exchanging integrals, substituting $\wt{x} = x + trz$, and noting that $x \in \mc{X}$ implies that $\wt{x} \in \Omega$.

@@

Suppose $f$ satisfies $|f(x') - f(x)| \leq M \|x - x\|$ for all $x,x' \in \mc{X}$. Then we can strengthen the high probability bound in Lemma~\ref{lem:graph_sobolev_seminorm} from $1 - \delta$ to $1 - \delta^2/n$, at the cost of only a constant factor in the upper bound on $f^{\top} \Lap_{n,r} f$.
\begin{proposition}
	\label{prop:graph_sobolev_seminorm_lipschitz}
	Let $r \geq C_0(\log n/n)^{1/d}$. For any $f$ such that $|f(x') - f(x)| \leq M \|x - x\|$ for all $x,x' \in \mc{X}$, with probability at least $1 - C\delta^2/n$ it holds that
	\begin{equation*}
	f^{\top} \Lap_{n,r} f \leq \biggl(\frac{1}{\delta} + C_2\biggr) n^2 r^{d + 2} M^2.
	\end{equation*}
\end{proposition}
